---
title: "My StellarCV"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(scholar)
library(ggplot2)
id <- ("DSmw-4YAAAAJ&hl")
knitr::opts_chunk$set(echo = TRUE)
```

## Summary  

My research focuses on the effectiveness of contemporary interventions for musculoskeletal conditions, such as low back pain. I am also interested in implementation research and digital health to improve healthcare services and health outcomes. I am a physiotherapist and an NHMRC Early Career Fellow (PhD awarded on 21 June 2017) at the Institute for Musculoskeletal Health. Since `r get_oldest_article(id)`, I have published `r get_num_articles(id)` peer-reviewed articles in `r get_num_distinct_journals(id)` distinct journals. The work I led is published in top ranking general medical (e.g. BMJ) and specialist journals (e.g. Annals of the Rheumatic Diseases). My papers have been cited `r sum((get_citation_history(id))$cites)` and a current h-index = `r predict_h_index(id)[[1,2]]`. My work is impactful, my article in BMJ had over 130k downloads (Altmetric score: 1,083), and my research in Annals of the Rheumatic Diseases had more than 300 media mentions (Altmetric score: 949), including the cover of The Times UK and research news in BMJ.

###Citation history:
```{r citations, echo=FALSE}
citation_history <- get_citation_history(id)
ggplot(data=citation_history, aes(x=year, y=cites)) + geom_bar(stat="identity")
```

```{r co-authors, echo=FALSE}
network <- get_coauthors(id)
plot_coauthors(network, size_labels = 5)
```

My publications:
```{r journal metrics, echo=FALSE}
my_publications <- get_publications(id)
journal_if <- get_impactfactor(journals=my_publications$journal, max.distance = 0.1)
my_publications <- cbind(my_publications, journal_if)
my_publications
```